Nail: A practical interface generator for data formats

### 2014-04-29 paper/osdi14/design.tex
Wrote dependencies

Our grammars are based on Parser Expression Grammars, describing

@@

\subsection{Basics}
Nail grammars contain parsers
\begin{figure}[tb]
\begin{tabular}{ll}
\toprule
\bf Syntax & \bf Semantics \\
\midrule
\texttt{int32} & 32-bit signed integer \\
\multirow{2}{*}{\texttt{uint4}}
  & 4-bit unsigned integer, \\
  & returned as an 8-bit value \\
\multirow{2}{*}{\texttt{uint8 | 1..3}}
  & 8-bit unsigned integer, \\
  & $1\leq x \leq 3$ \\
\multirow{2}{*}{\texttt{uint16 | ..512}}
  & unsigned 16-bit integer, \\
  & $x \leq 512$ \\
\multirow{2}{*}{\texttt{int32 | [1,255,512]}}
  & signed 32 bit integer, \\
  & $x \in \{ 1, 255, 512 \}$ \\
\bottomrule
\end{tabular}
\caption{Example Nail grammars for integer values.}
\label{fig:range}
\end{figure}

\paragraph{Integers and Constraints}
Nail's fundamental 
The elementary parsers of Nail are the same as those of Hammer, signed
and unsigned integers with arbitrary lengths up to 64 bits.  Note that is
possible to define parsers for sub-byte lengths, e.g. to parse the 4-bit
data offset within the TCP header; in Nail's syntax.  Integer parsers
return their value in the smallest appropriately sized machine integer
type; e.g., a 24-bit integer is stored in a 32-bit wide variable.

Integer parsers can be constrained to fall either within an (inclusive)
range of values or be an element of a set of allowed values.
Figure~\ref{fig:range} shows several examples.
Invalid values or prematurely reaching the end of input will raise an
error when parsing input or generating output, and abort the procedure.

\paragraph{Sequence.}

Nail's fundamental concept is the structure combinator. It contains a list of
named parsers and unnamed constant parsers. The parser invokes each field 
in sequence and returns a structure containing the result of each parser.
For example, Figure~\ref{fig:dns-struct} shows the structure combinator
from a part of the grammar for DNS packets, along with the data model
corresponding to it.

@@

\begin{minipage}{0.45\columnwidth}
\begin{verbatim}
header = {
  id uint16
  qr uint1
  opcode uint4
  aa uint1 
  tc uint1
  rd uint1
  ra uint1
  uint3 = 0
  rcode uint4
}
\end{verbatim} 
\end{minipage}
~
\begin{minipage}{0.45\columnwidth}
\begin{verbatim}
struct header {
  uint16_t id;
  uint8_t qr;
  uint8_t opcode;
  uint8_t aa;
  uint8_t tc;
  uint8_t rd;
  uint8_t ra;
  uint8_t rcode;
};
\end{verbatim} 
\end{minipage}

@@

\paragraph{Repetition.}

\paragraph{Semantic choice.}

We extend a parsing expression grammar's ordered choice combinator with
a tag for each choice. The parser
attempts to parse each option in the order they are specified in the field and
stores the result in a tagged union. If an option fails, the parser backtracks
to the beginning of the choice combinator's input. Care must be taken that the
choices do not overlap, because Nail always picks the first successfully
parsed choice. If two options overlap, generated output for the latter option is
not necessarily understood identically by the parser. However, actual data
formats are usually not ambiguous in this sense.
Figure~\ref{fig:choice} demonstrates a simple choice combinator.

@@

\subsection{Constant parsers}

Nail also features \emph{constant parsers}, which do not affect the internal
representation. Constant parsers can appear instead of structure fields and as
separators in the sepBy combinator.

The simplest constant parser is an integer or array of integers with fixed
value; for example, \texttt{uint8=0}, or \texttt{many uint8=[1,2]}. A convenience notation
for strings is also supported: \texttt{many uint8 = "foo"}.

\paragraph{Wrap combinator.} When implementing real protocols with Nail, we often found that
structures that consist of many constant parsers and only one named field. This pattern is
common in binary protocols which use fixed headers to denote the type of data
structure to be parsed.  In order to keep the internal representation cleaner,
we introduced the wrap combinator, which takes a sequence of parsers containing
exactly one non-constant parser. The parser and generator act as though the wrap
combinator was a sequence of parsers, but the data model does not wrap the
single value in another structure, making the application-visible representation
(and thus application code) more concise.

For example, \texttt{<uint8='"'; many int8 | 'a'..'z'; uint8='"'>} parses a quoted
lowercase word into an array, excluding the quotation marks.

\paragraph{Constant combinators.}
In some protocols, there might be many ways to represent the same constant field
and there is no semantic difference between the different syntactic representations.
To support this pattern, Nail allows developers to use choice and repetition
combinators together with constant fields, such as
\texttt{many (uint8=' ')} (representing any number of space characters), or
\texttt{|| uint8 = 0x90 || uint16 = 0x1F0F} (parsing two of the many representations of NOP on the
x86 architecture). Note that constant may have varying lengths.
This is particularly useful for handling padding or whitespace.

As discussed above, choosing to use these combinators on constant parsers
removes the bijection between byte-strings and our data model, as there are
multiple byte-strings that correspond to the same internal data structure and
the generator has to choose one of these representations. As such, constant
combinators are the generator dual of ambiguous choice combinators in the
parser, because they lead to ambiguities in the generator.

\subsection{Dependent fields}
Another problem for parser generators is that binary protocols often contain
length and offset fields. Conventional parsing algorithms can, in principle,
deal with
bounded offset fields: a finite automaton can count a bounded integer, and we
can feed the (finite) input multiple times to the finite automaton. However,
this implementation is both time-inefficient (it feeds many bytes into the
automaton that will just be skipped) and very cumbersome to express with
current parser generators. Therefore, if languages with offset fields need
to be parsed
with parser generators, the only currently practical way is to add ad-hoc hacks
such as changing the input pointer of the generated parser on the fly, as part
of the code in the semantic action for the offset field.

Nail will properly support both offset and length fields and much of the
following discussion applies to both, although the current prototype only
implements lengths, which we will focus on.

We call length or offset fields \textit{dependent fields}, because during
parsing, another parser depends on them, and while generating output, their
value depends on some other structure in the data model. Dependency fields
appear in a structure combinator as would any other integer field, but
their name begins with an \texttt{@} sign.  A dependency field has to
appear in the grammar before it can be used.

Dependency fields are not exposed in the data model, but instead are
transparently computed.  This frees the developer from checking that
these fields are correct (for input) or having to keep their values in
sync with the rest of the data structure (for output).

\paragraph{Length fields.}

The length combinator, \texttt{n_of}, takes a dependency field $n$
and a parser, evaluates the parser exactly $n$ times (i.e., setting
the number of iterations to be the $n$ field's value), and returns
an array of the parser's values. When generating output, it emits
the array and writes its length to the dependency field.

\paragraph{Offsets.}

The \texttt{offset} combinator takes a dependency field and a parser. It
moves the parser to the position specified in the offset field and
invokes the inner parser, and then moves the input back to its original
position.  While generating output, all structures referred to by offset
are generated after the main structure and the dependent offset fields
are patched up.

\paragraph{Checksums.}

In many data formats, some values depend on external representation,
such as checksums and cryptographic signatures.  While it would be
possible to extend our constraint language to be powerful enough to
support such constructs, we would essentially be building a separate,
Turing-complete language that has all the same pitfalls existing programs
have.  Therefore, we intend to allow the programmer to carefully escape
Nail's programming model and write a function that takes a pointer to
the dependent value and a range of bytes, using the \texttt{raw_depend}
combinator.

For example, we imagine the following grammar could be used to represent
a sequence of bytes \texttt{data} followed by its CRC32 checksum:

\begin{verbatim}
data many uint8; @checksum uint32
raw_depend @checksum data crc32
\end{verbatim}

\noindent
where \texttt{crc32} is a function supplied by the application, with
the following signature:

\begin{verbatim}
bool crc32(uint32_t *out, uint8_t *in);
\end{verbatim}

Because this feature compromises Nail's security guarantees, it should
only be used in limited circumstances and with carefully prepared checksum
functions.  This feature is not implemented in the current prototype.

>>>>

@@

\subsection{Basics}
Nail grammars are a set of rules. Each rule assigns a parser, which can be a reference to another
rule, a trivial parser describing an integer of a certain width or a combinator that combines
multiple parsers in some way. We provide the most common combinators familiar from other parser
combinator libraries, such as Parsec\cite{LeijenMeijer:parsec} and Hammer\cite{hammer-parser}.
However, we extend the sequence and choice combinators normally found in parser combinator libraries
with \emph{semantic labels} that name fields in the internal models. The syntax described by a Nail
grammar does not depend on these semantic labels.

\paragraph{Integers and Constraints}
\begin{figure}[tb]
\begin{tabular}{ll}
\toprule
\bf Syntax & \bf Semantics \\
\midrule
\texttt{int32} & 32-bit signed integer \\
\multirow{2}{*}{\texttt{uint4}}
  & 4-bit unsigned integer, \\
  & returned as an 8-bit value \\
\multirow{2}{*}{\texttt{uint8 | 1..3}}
  & 8-bit unsigned integer, \\
  & $1\leq x \leq 3$ \\
\multirow{2}{*}{\texttt{uint16 | [1,2]}}
  & unsigned 16-bit integer, \\
  & $x \in \{1,2\}$ \\
\multirow{2}{*}{\texttt{int32 | [1,5..255,512]}}
  & signed 32 bit integer, \\
  & $x \in \{ 1, 512 \} \vee 5\leq x\leq 255$ \\
\bottomrule
\end{tabular}
\caption{Example Nail grammars for integer values.}
\label{fig:range}
\end{figure}

Nail's fundamental parsers recognise signed or unsigned with arbitrary lengths up to 64 bits, an
approach popularised by the Hammer framework.\cite{hammer-parser}  
Note that is possible to define parsers for sub-byte lengths, e.g. to parse the 4-bit
data offset within the TCP header.  In the internal representation, integer values are represented
by the nearest usable integer size, for example a 24-bit unsigned integer will be stored in an
unsigned 32-bit double word.

The grammar can also express a constraint on an integer field. The current version of Nail expresses
constraints as a set of permissible values or value ranges. Extending the Nail language and
implementation to support richer constraints languages would be relatively trivial, however we have
found that the current syntax covers permissible values within existing protocols correctly and
concisely.

Figure~\ref{fig:range} shows several examples.

\paragraph{S.}

\paragraph{Structures.}

@@

\begin{minipage}{0.45\columnwidth}
\begin{verbatim}
dns_header = {
  id uint16
  qr uint1
  opcode uint4
  aa uint1 
  tc uint1
  rd uint1
  ra uint1
  uint3 = 0
  rcode uint4
}
\end{verbatim} 
\end{minipage}
~
\begin{minipage}{0.45\columnwidth}
\begin{verbatim}
struct dns_header {
  uint16_t id;
  uint8_t qr;
  uint8_t opcode;
  uint8_t aa;
  uint8_t tc;
  uint8_t rd;
  uint8_t ra;
  uint8_t rcode;
};
\end{verbatim} 
\end{minipage}

@@

Nail provides a structure combinator with semantic labels instead of the sequence combinator that
other parser combinator libraries use to capture structures in data formats. 
The structure combinator consists of a sequence of fields, typically consisting of a label and a
parser that describes the contents of that field. Other field types will be described below.
 The syntax of the structure combinator is inspired by the Go language\cite{golang}, with field names preceding their definition.
In our opinion, this syntax is easier to read than the widespread C-style structure and type
declarations.

A sample grammar for a DNS header and the corresponding C data type the Nail parser produces, are
shown in Figure~\ref{fig:dns-struct}.

\paragraph{Constants.}
In some cases, not all bytes in a structure actually contain information, such as magic numbers or
reserved fields. Those fields can be represented in Nail grammars by constant fields in structures.
Constant fields do not correspond to a field in the internal model, but they are validated during
parsing and generated during output.  Constants can either have integer values, such as
\texttt{uint3=0} or string values for text-based protocols, e.g. \texttt{many uint8 = ``Foo''}.

In some protocols, there might be many ways to represent the same constant field
and there is no semantic difference between the different syntactic representations.
Nail therefore allows repeated constants, such as \texttt{many (uint8=' ')}, which parses any number of space characters, or
\texttt{|| uint8 = 0x90 || uint16 = 0x1F0F}, which parses two of the many representations for X86
NOP instructions, which are used as padding between basic blocks in an executable.

As discussed above, choosing to use these combinators on constant parsers
removes the bijection between byte-strings and our data model, as there are
multiple byte-strings that correspond to the same internal data structure and
the generator has to choose one of these representations.
\paragraph{Wrap combinator.} 
When implementing real protocols with Nail, we often found that
structures that consist of many constant parsers and only one named field. This pattern is
common in binary protocols which use fixed headers to denote the type of data
structure to be parsed.  In order to keep the internal representation cleaner,
we introduced the wrap combinator, which takes a sequence of parsers containing
exactly one non-constant parser. The parser and generator act as though the wrap
combinator was a sequence of parsers, but the data model does not wrap the
single value in another structure, making the application-visible representation
(and thus application code) more concise.

For example, \texttt{word= <uint8='"'; many int8 | 'a'..'z'; uint8='"'>} parses a quoted
lowercase word into an array.

\paragraph{References.}
To support recursive structures, we include a reference combinator \texttt{*}, which is
syntactically equivalent to directly including the parser, but in the internal model adds a level of
indirection to the value. This allows recursive structures to be parsed, for example, balanced
parentheses could be parsed as follows: \texttt{paren = < uint8 ="("; optional *paren ;uint8=")">}

\paragraph{Choices.}
Our choice combinator takes multiple labelled parsers and tries each of them in turn, backtracking
to the initial position if an option fails. This behaviour for the choice combinator, the defining
feature of Parser Expression Grammars\cite{ford2002packrat}, resolves any ambiguities explicitly.
Internally, the choice combinator represents choices as tagged unions.

If two options the same string could be parser by two options, generated output for the latter
option is not necessarily understood identically by the parser. However, actual data formats are
usually not ambiguous in this sense. Figure~\ref{fig:choice} demonstrates a simple choice
combinator.

Nail also includes an \texttt{optional} combinator, which attempts to recognise a value, but succeeds
without consuming input when it cannot recognise that value. Syntactically, \texttt{optional} is
equivalent to a choice between the parser and an empty structure, but in the internal model it is
more concisely represented as a reference that is null when the parser fails.

@@

\subsection{Dependent fields}

Data formats often contain values that are determined by other values or the layout of information,
such as checksums, duplicated information  or offset and  length fields.
We represent such as values with \emph{dependent fields} and handle them transparently during
parsing and generation without exposing them to the internal model.

Dependent fields are defined within a structure like normal fields, but their name starts with an \@-sign. 
A dependent field is in scope and can be referred to by the definition of all subsequent fields in the same structure.

During parsing, dependent fields are parsed just like other fields, but instead of storing their
value in a structure that will be returned to the programmer, the parser stores the value in a
temporary location. Thereafter, the value can be referenced in the grammar.

When generating output, Nail visits a dependent field twice. When generating the fields of a
structure, it will reserve space for the dependent field in the output, but not write a value. When
the dependent field goes out of scope, the generator will backtrack to this space and write the
dependent fields value.

Nail only provides one built-in combinator, \texttt{n_of} that uses dependency fields, which is used
for count fields. For example, DNS labels are encoded as Pascal-style strings - a length followed by
the value of the label. The Nail grammar for DNS packets in Figure~\ref{fig:dns-full} represents
this pattern as follows:

\begin{figure}[tb]
\begin{verbatim}
{ @length uint8 | 1..64
  label n_of @length uint8 }
\end{verbatim}
\caption{Nail grammar for uncompressed DNS labels.}
\end{figure}

Other dependencies, such as offset fields or checksums are not handled directly by combinators, but
through stream transformation.

\subsection{Input streams and Transformations.}

% Data formats often contain redundant information, such as checksums or duplicated values.
% Conventional parsers expose all this information and validate it manually, which can lead to bugs.

% Another problem for interface generators is that binary protocols often contain length and offset
% fields. Conventional parsing algorithms can, in principle, deal with bounded offset fields - a finite
% automaton can count a bounded integer, by introducing a state for each value. However, such grammars
% are very large, making the state-machine implementation inefficient and the grammar very complicated.

% Nail will properly support both offset and length fields and much of the
% following discussion applies to both, although the current prototype only
% implements lengths, which we will focus on.

% We call length or offset fields \textit{dependent fields}, because during
% parsing, another parser depends on them, and while generating output, their
% value depends on some other structure in the data model. Dependency fields
% appear in a structure combinator as would any other integer field, but
% their name begins with an \texttt{@} sign.  A dependency field has to
% appear in the grammar before it can be used.

% Dependency fields are not exposed in the data model, but instead are
% transparently computed.  This frees the developer from checking that
% these fields are correct (for input) or having to keep their values in
% sync with the rest of the data structure (for output).

% \paragraph{Length fields.}

% The length combinator, \texttt{n_of}, takes a dependency field $n$
% and a parser, evaluates the parser exactly $n$ times (i.e., setting
% the number of iterations to be the $n$ field's value), and returns
% an array of the parser's values. When generating output, it emits
% the array and writes its length to the dependency field.

% \paragraph{Offsets.}

% The \texttt{offset} combinator takes a dependency field and a parser. It
% moves the parser to the position specified in the offset field and
% invokes the inner parser, and then moves the input back to its original
% position.  While generating output, all structures referred to by offset
% are generated after the main structure and the dependent offset fields
% are patched up.

% \paragraph{Checksums.}

% In many data formats, some values depend on external representation,
% such as checksums and cryptographic signatures.  While it would be
% possible to extend our constraint language to be powerful enough to
% support such constructs, we would essentially be building a separate,
% Turing-complete language that has all the same pitfalls existing programs
% have.  Therefore, we intend to allow the programmer to carefully escape
% Nail's programming model and write a function that takes a pointer to
% the dependent value and a range of bytes, using the \texttt{raw_depend}
% combinator.

% For example, we imagine the following grammar could be used to represent
% a sequence of bytes \texttt{data} followed by its CRC32 checksum:

% \begin{verbatim}
% data many uint8; @checksum uint32
% raw_depend @checksum data crc32
% \end{verbatim}

% \noindent
% where \texttt{crc32} is a function supplied by the application, with
% the following signature:

% \begin{verbatim}
% bool crc32(uint32_t *out, uint8_t *in);
% \end{verbatim}

% Because this feature compromises Nail's security guarantees, it should
% only be used in limited circumstances and with carefully prepared checksum
% functions.  This feature is not implemented in the current prototype.

### 2014-04-29 paper/osdi14/impl.tex
Wrote dependencies

The current prototype of the Nail parser generator supports the C programming
language and top-down parsers. Options for C++ STL data models and emitting
Packrat parser~\cite{packrat-parsing:icfp02} are under development. In
this section, we will discuss some particular features of our parser
implementation.

@@

\input{fig-utf16}

@@

A generated Nail parser makes two passes through the input: the first to
validate and recognize the input, and the second to bind this data to the internal
model. Currently the parser is a straightforward top-down parser, although
facilities have been made to add Packrat parsing to achieve linear parsing
times.

@@

Many security vulnerabilities can occur when heap allocations are done
improperly. Therefore, just like Hammer, Nail avoids using the heap as much as
possible, using a custom arena allocator and allocating only fixed-size blocks
from the system allocator (malloc). However, Nail extends upon Hammer's approach and uses two
arenas for each parsed input. One arena is used for intermediate results and is
released (and zeroed) after parsing completes, whereas the other arena is used only
for allocating the result, and has to be freed by the programmer.

@@

Most parser generators, such as Bison, do not have to dynamically allocate
temporary data, as they evaluate a semantic action on every rule. However, as
our goal is to perform as little computation as possible before the input
has been validated, and we do not want to mix temporary objects with the
results of our parse, we use an append-only trace to store intermediate parser
results.

@@

\paragraph{Dependency fields.}

During parsing, dependency fields occur before the context in which they are
used. The parser stores their values and retrieves them afterwards when
encountering the combinator that uses them. When generating output, the
dependency field is first filled with a filler value, then later when the first
combinator that determines this fields value is encountered, the field is
overwritten. Any further combinators using this dependency will then validate
that the dependency field is correct.

>>>>

The current prototype of the Nail parser generator supports the C programming
language and top-down parsers. Options for C++ STL data models and emitting
Packrat parsers~\cite{packrat-parsing:icfp02} are under development. In
this section, we will discuss some particular features of our parser
implementation.

@@

@@

A generated Nail parser makes two passes through the input: the first to
validate and recognize the input, and the second to bind this data to the internal
model. Currently the parser is a straightforward top-down parser, although
preparations have been made to add Packrat parsing to achieve linear parsing
times.

@@

Many security vulnerabilities can occur when heap allocations are done improperly. Therefore, just
like Hammer, Nail avoids using the heap as much as possible, using a custom arena allocator and
allocating only fixed-size blocks from the system allocator (malloc). However, Nail extends upon
Hammer's approach and uses two arenas for each parsed input. One arena is used for intermediate
structures, including dependency fields and any temporary streams, and is released (and zeroed)
after parsing completes, whereas the other arena is used only for allocating the result, and has to
be freed by the programmer.

@@

Most parser generators, such as Bison, do not have to dynamically allocate temporary data on the
heap, as they evaluate a semantic action on every rule. However, as our goal is to perform as little
computation as possible before the input has been validated, and we do not want to mix temporary
objects with the results of our parse, we use an append-only trace to store intermediate parser
results.

@@

% \paragraph{.}

% During parsing, dependency fields occur before the context in which they are
% used. The parser stores their values and retrieves them afterwards when
% encountering the combinator that uses them. When generating output, the
% dependency field is first filled with a filler value, then later when the first
% combinator that determines this fields value is encountered, the field is
% overwritten. Any further combinators using this dependency will then validate
% that the dependency field is correct.

### 2014-04-29 paper/osdi14/intro.tex
Wrote dependencies

Third, data formats, for example PNG or PDF, contain features that are hard to represent with
existing parser generators. Some features, such as length and checksum fields, require the parser to
keep additional state. More complicated formats incorporate offset fields that require the parser to
reposition its input stream or consume the same input multiple times. In some cases, such as with
compressed data, very complicated transformations on the external format are necessary before it can
be understood. State-of-the-Art parser generators provide at most limited, unelegant facilities for
such features, so programmers are forced to manually writing control code to handle them, such as
moving the parsers input stream, looping over the invocation of a sub-parser or computing a checksum
over raw input bytes. Besides leaving much room for errors with offset arithmetic, such code is
usually not reusable when generating output.

\XXX[Motivate Stream transforms better]

This paper presents the initial design and implementation of Nail, a parser
generator that greatly reduces the programmer effort required to use a
grammar-based parser. Nail addresses the above three challenges with several key
ideas.

@@

\XXX[Currently, Nail always makes a default choice when
there are multiple options to express a constant, however Nail could be extended
to allow a grammar-specific plug-in to make these choices, say for faster
alignment, streaming applications when data is not ready, or visual appearance in
human-readable protocols.]

 However, Nail allows \emph{constants} in the
external format to have multiple representations if they should not affect the
semantics of the data. For example, in a text protocol, the amount of
white-space separating tokens should not affect the meaning of the data and
consequently Nail does not expose it to the application. As long as
constants are only used for their intended purpose of representing syntax-only
features, the generated output will have the same semantics as the parsed input.

Third, Nail introduces two abstractions, \emph{dependent fields} and \emph{stream transforms}, to
elegantly handle problematic features of data formats. Dependent fields are fields in the protocol
whose value depends in some way on the value or layout of other parts of the protocol, such as
length, offset and checksum fields. \XXX[Stream transforms allow the programmer to write a function
that produces one or more virtual streams from one or more virtual streams and the values of
dependent fields.]

>>>>

Third, many data formats contain redundancies, such as repeating information in multiple structures.
Applications usually do not explicitly check for consistency, and if different applications use
different instances of the same value, an attacker can craft input that causes inconsistencies.
Furthermore, security vulnerability can occur when an application assumes two repetitions of the
same data to be consistent.

Finally, data formats, for example PNG or PDF, contain features that are hard to represent with
existing parser generators. Some features, such as length and checksum fields, require the parser to
keep additional state. More complicated formats incorporate offset fields that require the parser to
reposition its input stream or consume the same input multiple times. In some cases, such as with
compressed data, very complicated transformations on the external format are necessary before it can
be understood. State-of-the-Art parser generators provide at most limited, unelegant facilities for
such features, so programmers are forced to manually writing control code to handle them, such as
moving the parsers input stream, looping over the invocation of a sub-parser or computing a checksum
over raw input bytes. Besides leaving much room for errors with offset arithmetic, such code is
usually not reusable when generating output.

This paper presents the initial design and implementation of Nail, a parser
generator that greatly reduces the programmer effort required to use a
grammar-based parser. Nail addresses the above four challenges with several key
ideas.

@@

% \XXX[Currently, Nail always makes a default choice when
% there are multiple options to express a constant, however Nail could be extended
% to allow a grammar-specific plug-in to make these choices, say for faster
% alignment, streaming applications when data is not ready, or visual appearance in
% human-readable protocols.]

%  However, Nail allows \emph{constants} in the
% external format to have multiple representations if they should not affect the
% semantics of the data. For example, in a text protocol, the amount of
% white-space separating tokens should not affect the meaning of the data and
% consequently Nail does not expose it to the application. As long as
% constants are only used for their intended purpose of representing syntax-only
% features, the generated output will have the same semantics as the parsed input.

Third, Nail introduces two abstractions, \emph{dependent fields} and \emph{structural transformations}, to
elegantly handle problematic features of data formats. Dependent fields are fields in the protocol
whose value depends in some way on the value or layout of other parts of the protocol, such as
length, offset and checksum fields. Structural transformations allow the programmer to write a pair
of functions that transforms the \XXX[TODO]
